Categorical Predictor Embeddings in Actuarial Modeling

### 2021-04-04 manuscript/manuscript.Rmd
fix caption

|dimension |value  |dimension |value  |dimension |value  |dimension |value  |
|:---------|:------|:---------|:------|:---------|:------|:---------|:------|
|e1        |-0.167 |e11       |-0.810 |e21       |-0.300 |e31       |-0.421 |
|e2        |-0.363 |e12       |1.380  |e22       |-0.194 |e32       |0.594  |
|e3        |-0.893 |e13       |-0.180 |e23       |-0.320 |e33       |1.681  |
|e4        |0.130  |e14       |-1.612 |e24       |-0.035 |e34       |1.668  |
|e5        |-1.588 |e15       |-1.327 |e25       |-1.128 |          |       |
|e6        |-0.123 |e16       |-0.965 |e26       |0.168  |          |       |
|e7        |-0.259 |e17       |-1.356 |e27       |-1.022 |          |       |
|e8        |0.324  |e18       |-0.061 |e28       |1.011  |          |       |
|e9        |-1.430 |e19       |-0.120 |e29       |-0.843 |          |       |
|e10       |-1.598 |e20       |-0.488 |e30       |-0.743 |          |       ||

@@

In this section, we focus on ways to visualize the learned embeddings. In the authors' experiences, oftentimes
the formats of the visualizations --- basic line and scatter plots --- even more so than the content of the data, is 
helpful in explaining the concept to stakeholders.

For Model 2, the neural network with one-dimensional embeddings, the task is simple: we can simply plot the levels
on a line, as in Figure \@ref(fig:occ-type). In the case of `flood_zone`, since we happen to have the luxury of knowing a
priori the meaning of the prefixes, we can plot them separately, as in Figure \@ref(fig:flood-zone) to see how the model 
mapped them.

```{r occ-type, echo=FALSE, fig.cap="Occupancy type", out.width = "80%", fig.align="center"}
knitr::include_graphics("images/occupancy_type.png")
```

```{r flood-zone, echo = FALSE, fig.cap="Flood zone embeddings", out.width = "60%", fig.align = "center"}
knitr::include_graphics("images/flood_zone.png")
```

>>>>

|dimension |value  |dimension |value  |dimension |value  |dimension |value  |
|:---------|:------|:---------|:------|:---------|:------|:---------|:------|
|e1        |-0.167 |e11       |-0.810 |e21       |-0.300 |e31       |-0.421 |
|e2        |-0.363 |e12       |1.380  |e22       |-0.194 |e32       |0.594  |
|e3        |-0.893 |e13       |-0.180 |e23       |-0.320 |e33       |1.681  |
|e4        |0.130  |e14       |-1.612 |e24       |-0.035 |e34       |1.668  |
|e5        |-1.588 |e15       |-1.327 |e25       |-1.128 |          |       |
|e6        |-0.123 |e16       |-0.965 |e26       |0.168  |          |       |
|e7        |-0.259 |e17       |-1.356 |e27       |-1.022 |          |       |
|e8        |0.324  |e18       |-0.061 |e28       |1.011  |          |       |
|e9        |-1.430 |e19       |-0.120 |e29       |-0.843 |          |       |
|e10       |-1.598 |e20       |-0.488 |e30       |-0.743 |          |       |

@@

In this section, we focus on ways to visualize the learned embeddings. In the authors' experiences, oftentimes
the formats of the visualizations---basic line and scatter plots---even more so than the content of the data, are 
helpful in explaining the concept to stakeholders.

For Model 2, the neural network with one-dimensional embeddings, the task is simple: we can simply plot the levels
on a line, as in Figure \@ref(fig:occ-type). In the case of `flood_zone`, where we happen to have the luxury of knowing
 a
priori the meaning of the prefixes, we can plot them separately, as in Figure \@ref(fig:flood-zone) to see how the
 model 
mapped them.

```{r occ-type, echo=FALSE, fig.cap="Learned embeddings of occupancy type visualized on a number line.", out.width = "80%", fig.align="center"}
knitr::include_graphics("images/occupancy_type.png")
```

```{r flood-zone, echo = FALSE, fig.cap="Learned embeddings of flood zone by prefix.", out.width = "60%", fig.align = "center"}
knitr::include_graphics("images/flood_zone.png")
```
